|

### 2018-01-08 article/Funk-Mullen.Spine-of-American-Law.Rmd
Re-run article PDF code

---
fontfamily:
- mathpazo
fontsize: 12pt
geometry:
- "margin=1in"
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
    template: article-template.tex
  word_document: 
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    pandoc_args: ["--smart"]
title: |
       | The Spine of American Law\: 
       | Digital Text Analysis and U.S. Legal Practice
author: 
- name: Kellen Funk
  affiliation: Princeton University
  email: kfunk@princeton.edu
- name: Lincoln Mullen
  affiliation: George Mason University
  email: lincoln@lincolnmullen.com
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
library(stringr)
library(scales)
library(textreuse)
source("../R/helper.R")
source("../R/section-matches.R")
source("../R/spectrogram.R")
load("../cache/corpus-lsh.rda")
load("../cache/network-graphs.rda")
set.seed(82893)
dir.create("../out/figures", recursive = TRUE, showWarnings = FALSE)
bw <- TRUE
```

>>>>

---
fontfamily:
- mathpazo
fontsize: 12pt
geometry:
- "margin=1in"
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash+smart'
    number_sections: False
    template: article-template.tex
title: |
       | The Spine of American Law\: 
       | Digital Text Analysis and U.S. Legal Practice
author: 
- name: Kellen Funk
  affiliation: Princeton University
  email: kfunk@princeton.edu
- name: Lincoln Mullen
  affiliation: George Mason University
  email: lincoln@lincolnmullen.com
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
library(stringr)
library(scales)
library(textreuse)
source("../R/helper.R")
source("../R/section-matches.R")
source("../R/spectrogram.R")
load("../cache/corpus-lsh.rda")
load("../cache/network-graphs.rda")
set.seed(82893)
dir.create("../out/figures", recursive = TRUE, showWarnings = FALSE)
bw <- FALSE
```
